\textbf{SPECFEM3D}\newline \textbf{Cartesian}\newline \textbf{User Manual}

### 2022-11-12 doc/USER_MANUAL/02_getting_started.tex
updates tex files (\\ to \newline) for better pandoc conversions to wiki pages

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.
You can also have a look at the configure script called:\\
\texttt{utils/Cray\_compiler\_information/configure\_SPECFEM\_for\_Piz\_Daint.bash}.

On SGI systems, \texttt{flags.guess} automatically informs \texttt{configure}
to insert `\texttt{`TRAP\_FPE=OFF}'' into the generated \texttt{Makefile}
in order to turn underflow trapping off.\\

You can add \texttt{-{}-enable-vectorization} to the configuration options to speed up the code in the fluid (acoustic) and elastic parts.
This works fine if (and only if) your computer always allocates a contiguous memory block for each allocatable array;
this is the case for most machines and most compilers, but not all. To disable this feature, use option \texttt{-{}-disable-vectorization}.
For more details see \href{https://github.com/SPECFEM/specfem3d/issues/81}{github.com/SPECFEM/specfem3d/issues/81} .
To check if that option works fine on your machine, run the code with and without it for an acoustic/elastic model and make sure the seismograms are identical.\\

Note that we use CUBIT (now called Trelis) to create meshes of hexahedra, but other packages
can be used as well, for instance GiD from \url{http://gid.cimne.upc.es}
or Gmsh from \url{http://geuz.org/gmsh} \citep{GeRe09}. Even mesh
creation packages that generate tetrahedra, for instance TetGen from
\url{http://tetgen.berlios.de}, can be used because each tetrahedron
can then easily be decomposed into four hexahedra as shown in the
picture of the TetGen logo at \url{http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif};
while this approach does not generate hexahedra of optimal quality,
it can ease mesh creation in some situations and it has been shown
that the spectral-element method can very accurately handle distorted
mesh elements \citep{OlSe11}.\\

The SPECFEM3D Cartesian software package relies on the SCOTCH library
to partition meshes created with CUBIT. METIS \citep{KaKu98a,KaKu98c,KaKu98b}
can also be used instead of SCOTCH if you prefer, by changing the parameter
\texttt{PARTITIONING\_TYPE} in the \texttt{DATA/Par\_file}. You will also then need to install
and compile Metis version 4.0 (do {*}NOT{*} install Metis version
5.0, which has incompatible function calls) and edit \texttt{Makefile.in}
and uncomment the METIS link flag in that file before running \texttt{configure}.\\

@@

When compiling the SCOTCH source code, if you get a message such as: "ld: cannot find -lz",
the Zlib compression development library is probably missing on your machine and you will need to install it or ask your system administrator to
do so. On Linux machines the package is often called "zlib1g-dev" or similar. (thus "sudo apt-get install zlib1g-dev" would install it)\\

To compile a serial version of the code for small meshes that fits
on one compute node and can therefore be run serially, run \texttt{configure}
with the \texttt{-{}-without-mpi} option to suppress all calls to
MPI.\\

For people who would like to run the package on Windows rather than on Unix machines, you can install Docker or VirtualBox (installing a Linux in VirtualBox in that latter case) and run it easily from inside that.\\

We recommend that you add {\texttt{ulimit -S -s unlimited}} to your
{\texttt{.bash\_profile}} file and/or {\texttt{limit stacksize
unlimited }} to your {\texttt{.cshrc}} file to suppress any potential
limit to the size of the Unix stack.\\

Beware that some cluster systems that run a recent version may not run and\slash compile an older version of the code. \\

When using dynamic fault in parallel with the developer version, we suggest you to set the configuration parameters
of \texttt{FAULT\_DISPL\_VELOC} and \texttt{FAULT\_SYNCHRONIZE\_ACCEL} as \texttt{.true.}.\\

@@

\noindent
SPECFEM3D now supports CUDA and HIP GPU acceleration.
When compiling for GPU cards, you can enable the CUDA version with:
\begin{verbatim}
  ./configure --with-cuda ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-cuda=cuda9 ..
\end{verbatim}
where for example \texttt{cuda4,cuda5,cuda6,cuda7,..} specifies the target GPU architecture of your card,
(e.g., with CUDA 9 this refers to Volta V100 cards), rather than the installed version of the CUDA toolkit.
Before CUDA version 5, one version supported basically one new architecture and needed a different kind of compilation.
Since version 5, the compilation has stayed the same, but newer versions supported newer architectures.
However at the moment, we still have one version linked to one specific architecture:
\begin{verbatim}
- CUDA 4 for Tesla,   cards like K10, Geforce GTX 650, ..
- CUDA 5 for Kepler,  like K20
- CUDA 6 for Kepler,  like K80
- CUDA 7 for Maxwell, like Quadro K2200
- CUDA 8 for Pascal,  like P100
- CUDA 9 for Volta,   like V100
- CUDA 10 for Turing, like GeForce RTX 2080
- CUDA 11 for Ampere, like A100
\end{verbatim}
So even if you have the new CUDA toolkit version 11, but you want to run on say a K20 GPU, then you would still configure with:
\begin{verbatim}
  ./configure --with-cuda=cuda5
\end{verbatim}
The compilation with the cuda5 setting chooses then the right architecture (\texttt{-gencode=arch=compute\_35,code=sm\_35} for K20 cards).\\

@@

OpenMP support can be enabled in addition to MPI. However, in many
cases performance will not improve because our pure MPI implementation
is already heavily optimized and thus the resulting code will in fact
be slightly slower. A possible exception could be IBM BlueGene-type
architectures.\\

\noindent
To enable OpenMP,  add the flag \texttt{-{}-enable-openmp} to the configuration:
\begin{verbatim}
./configure --enable-openmp ..
\end{verbatim}
This will add the corresponding OpenMP flag for the chosen Fortran compiler.\\

@@

\item [{\texttt{FLAGS\_CHECK}}] Compiler flags.
\end{description}
%
The configuration script automatically creates for each executable
a corresponding \texttt{Makefile} in the \texttt{src/} subdirectory.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.\\

Now that you have set the compiler information, you need to select
a number of flags in the \texttt{setup/constants.h} file depending on your
system:
\begin{description}
\item [{\texttt{LOCAL\_PATH\_IS\_ALSO\_GLOBAL}}] Set to \texttt{.false.}
on most cluster applications. For reasons of speed, the (parallel)
distributed database generator typically writes a (parallel) database
for the solver on the local disks of the compute nodes. Some systems
have no local disks, e.g., BlueGene or the Earth Simulator, and other
systems have a fast parallel file system, in which case this flag
should be set to \texttt{.true.}. Note that this flag is not used
by the database generator or the solver; it is only used for some
of the post-processing.
\end{description}
%
The package can run either in single or in double precision mode.
The default is single precision because for almost all calculations
performed using the spectral-element method using single precision
is sufficient and gives the same results (i.e. the same seismograms);
and the single precision code is faster and requires exactly half
as much memory. Select your preference by selecting the appropriate
setting in the \texttt{setup/constants.h} file:
\begin{description}
\item [{\texttt{CUSTOM\_REAL}}] Set to \texttt{SIZE\_REAL} for single precision
and \texttt{SIZE\_DOUBLE} for double precision.
\end{description}
%
In the \texttt{precision.h} file:
\begin{description}
\item [{\texttt{CUSTOM\_MPI\_TYPE}}] Set to \texttt{MPI\_REAL} for single
precision and \texttt{MPI\_DOUBLE\_PRECISION} for double precision.
\end{description}
%
On many current processors (e.g., Intel, AMD, IBM Power), single precision
calculations are significantly faster; the difference can typically
be 10\% to 25\%. It is therefore better to use single precision. What
you can do once for the physical problem you want to study is run
the same calculation in single precision and in double precision on
your system and compare the seismograms. If they are identical (and
in most cases they will), you can select single precision for your
future runs.\\

@@

\noindent
Installation instructions for IBM BlueGene (from April 2013):\\

@@

\noindent The most relevant are the -qarch and -qtune flags, otherwise
if these flags are set to ``auto'' then they are wrongly assigned
to the architecture of the frond-end node, which is different from
that on the compute nodes. You will need to set these flags to the
right architecture for your BlueGene compute nodes, which is not necessarily
``qp''; ask your system administrator. On some machines if is necessary
to use -O2 in these flags instead of -O3 due to a compiler bug of
the XLF version installed. We thus suggest to first try -O3, and then
if the code does not compile or does not run fine then switch back
to -O2. The debug flags (-g, -qfullpath) do not influence performance
but are useful to get at least some insights in case of problems.\\

\noindent Before running \texttt{configure}, select the XL Fortran
compiler by typing \texttt{module load bgq-xl/1.0} or \texttt{module
load bgq-xl} (another, less efficient option is to load the GNU compilers
using \texttt{module load bgq-gnu/4.4.6} or similar).\\

@@

\noindent \underline{Older installation instruction for IBM BlueGene, from 2011:}\\

@@

\begin{enumerate}
\setcounter{enumi}{-1}
\item Install \texttt{Doxygen} \underline{and} \texttt{graphviz} (the two are usually in the package manager of classic Linux distribution).
\item Run in the terminal : \texttt{doxygen -g}, which creates a \texttt{Doxyfile} that tells doxygen what you want it to do.
\item Edit the Doxyfile. Two Doxyfile-type files have been already committed in the directory \\
\noindent \texttt{specfem3d/doc/Call\_trees}:

@@

If you want to develop new features in the code, and/or if you want to make small changes, improvements, or bug fixes, you are very welcome to contribute. To do so, i.e. to access the development branch of the source code with read/write access (in a safe way, no need to worry too much about breaking the package, there are CI tests based on BuildBot, Travis-CI and Jenkins in place that are checking and validating all new contributions and changes), please visit this Web page:\\
\url{https://github.com/SPECFEM/specfem3d/wiki}

>>>>

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.
You can also have a look at the configure script called:\newline
\texttt{utils/Cray\_compiler\_information/configure\_SPECFEM\_for\_Piz\_Daint.bash}.

On SGI systems, \texttt{flags.guess} automatically informs \texttt{configure}
to insert `\texttt{`TRAP\_FPE=OFF}'' into the generated \texttt{Makefile}
in order to turn underflow trapping off.\newline

You can add \texttt{-{}-enable-vectorization} to the configuration options to speed up the code in the fluid (acoustic) and elastic parts.
This works fine if (and only if) your computer always allocates a contiguous memory block for each allocatable array;
this is the case for most machines and most compilers, but not all. To disable this feature, use option \texttt{-{}-disable-vectorization}.
For more details see \href{https://github.com/SPECFEM/specfem3d/issues/81}{github.com/SPECFEM/specfem3d/issues/81} .
To check if that option works fine on your machine, run the code with and without it for an acoustic/elastic model and make sure the seismograms are identical.\newline

Note that we use CUBIT (now called Trelis) to create meshes of hexahedra, but other packages
can be used as well, for instance GiD from \url{http://gid.cimne.upc.es}
or Gmsh from \url{http://geuz.org/gmsh} \citep{GeRe09}. Even mesh
creation packages that generate tetrahedra, for instance TetGen from
\url{http://tetgen.berlios.de}, can be used because each tetrahedron
can then easily be decomposed into four hexahedra as shown in the
picture of the TetGen logo at \url{http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif};
while this approach does not generate hexahedra of optimal quality,
it can ease mesh creation in some situations and it has been shown
that the spectral-element method can very accurately handle distorted
mesh elements \citep{OlSe11}.\newline

The SPECFEM3D Cartesian software package relies on the SCOTCH library
to partition meshes created with CUBIT. METIS \citep{KaKu98a,KaKu98c,KaKu98b}
can also be used instead of SCOTCH if you prefer, by changing the parameter
\texttt{PARTITIONING\_TYPE} in the \texttt{DATA/Par\_file}. You will also then need to install
and compile Metis version 4.0 (do {*}NOT{*} install Metis version
5.0, which has incompatible function calls) and edit \texttt{Makefile.in}
and uncomment the METIS link flag in that file before running \texttt{configure}.\newline

@@

When compiling the SCOTCH source code, if you get a message such as: "ld: cannot find -lz",
the Zlib compression development library is probably missing on your machine and you will need to install it or ask your system administrator to
do so. On Linux machines the package is often called "zlib1g-dev" or similar. (thus "sudo apt-get install zlib1g-dev" would install it)\newline

To compile a serial version of the code for small meshes that fits
on one compute node and can therefore be run serially, run \texttt{configure}
with the \texttt{-{}-without-mpi} option to suppress all calls to
MPI.\newline

For people who would like to run the package on Windows rather than on Unix machines, you can install Docker or VirtualBox (installing a Linux in VirtualBox in that latter case) and run it easily from inside that.\newline

We recommend that you add {\texttt{ulimit -S -s unlimited}} to your
{\texttt{.bash\_profile}} file and/or {\texttt{limit stacksize
unlimited }} to your {\texttt{.cshrc}} file to suppress any potential
limit to the size of the Unix stack.\newline

Beware that some cluster systems that run a recent version may not run and\slash compile an older version of the code. \newline

When using dynamic fault in parallel with the developer version, we suggest you to set the configuration parameters
of \texttt{FAULT\_DISPL\_VELOC} and \texttt{FAULT\_SYNCHRONIZE\_ACCEL} as \texttt{.true.}.\newline

@@

\noindent
SPECFEM3D now supports CUDA and HIP GPU acceleration.
When compiling for GPU cards, you can enable the CUDA version with:
\begin{verbatim}
  ./configure --with-cuda ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-cuda=cuda9 ..
\end{verbatim}
where for example \texttt{cuda4,cuda5,cuda6,cuda7,..} specifies the target GPU architecture of your card,
(e.g., with CUDA 9 this refers to Volta V100 cards), rather than the installed version of the CUDA toolkit.
Before CUDA version 5, one version supported basically one new architecture and needed a different kind of compilation.
Since version 5, the compilation has stayed the same, but newer versions supported newer architectures.
However at the moment, we still have one version linked to one specific architecture:
\begin{verbatim}
- CUDA 4 for Tesla,   cards like K10, Geforce GTX 650, ..
- CUDA 5 for Kepler,  like K20
- CUDA 6 for Kepler,  like K80
- CUDA 7 for Maxwell, like Quadro K2200
- CUDA 8 for Pascal,  like P100
- CUDA 9 for Volta,   like V100
- CUDA 10 for Turing, like GeForce RTX 2080
- CUDA 11 for Ampere, like A100
\end{verbatim}
So even if you have the new CUDA toolkit version 11, but you want to run on say a K20 GPU, then you would still configure with:
\begin{verbatim}
  ./configure --with-cuda=cuda5
\end{verbatim}
The compilation with the cuda5 setting chooses then the right architecture (\texttt{-gencode=arch=compute\_35,code=sm\_35} for K20 cards).\newline

@@

OpenMP support can be enabled in addition to MPI. However, in many
cases performance will not improve because our pure MPI implementation
is already heavily optimized and thus the resulting code will in fact
be slightly slower. A possible exception could be IBM BlueGene-type
architectures.\newline

\noindent
To enable OpenMP,  add the flag \texttt{-{}-enable-openmp} to the configuration:
\begin{verbatim}
./configure --enable-openmp ..
\end{verbatim}
This will add the corresponding OpenMP flag for the chosen Fortran compiler.\newline

@@

\item [{\texttt{FLAGS\_CHECK}}] Compiler flags.
\end{description}
%
The configuration script automatically creates for each executable
a corresponding \texttt{Makefile} in the \texttt{src/} subdirectory.
The \texttt{Makefile} contains a number of suggested entries for various
compilers, e.g., Portland, Intel, Absoft, NAG, and Lahey. The software
has run on a wide variety of compute platforms, e.g., various PC clusters
and machines from Sun, SGI, IBM, Compaq, and NEC. Select the compiler
you wish to use on your system and choose the related optimization
flags. Note that the default flags in the \texttt{Makefile} are undoubtedly
not optimal for your system, so we encourage you to experiment with
these flags and to solicit advice from your systems administrator.
Selecting the right compiler and optimization flags can make a tremendous
difference in terms of performance. We welcome feedback on your experience
with various compilers and flags.\newline

Now that you have set the compiler information, you need to select
a number of flags in the \texttt{setup/constants.h} file depending on your
system:
\begin{description}
\item [{\texttt{LOCAL\_PATH\_IS\_ALSO\_GLOBAL}}] Set to \texttt{.false.}
on most cluster applications. For reasons of speed, the (parallel)
distributed database generator typically writes a (parallel) database
for the solver on the local disks of the compute nodes. Some systems
have no local disks, e.g., BlueGene or the Earth Simulator, and other
systems have a fast parallel file system, in which case this flag
should be set to \texttt{.true.}. Note that this flag is not used
by the database generator or the solver; it is only used for some
of the post-processing.
\end{description}
%
The package can run either in single or in double precision mode.
The default is single precision because for almost all calculations
performed using the spectral-element method using single precision
is sufficient and gives the same results (i.e. the same seismograms);
and the single precision code is faster and requires exactly half
as much memory. Select your preference by selecting the appropriate
setting in the \texttt{setup/constants.h} file:
\begin{description}
\item [{\texttt{CUSTOM\_REAL}}] Set to \texttt{SIZE\_REAL} for single precision
and \texttt{SIZE\_DOUBLE} for double precision.
\end{description}
%
In the \texttt{precision.h} file:
\begin{description}
\item [{\texttt{CUSTOM\_MPI\_TYPE}}] Set to \texttt{MPI\_REAL} for single
precision and \texttt{MPI\_DOUBLE\_PRECISION} for double precision.
\end{description}
%
On many current processors (e.g., Intel, AMD, IBM Power), single precision
calculations are significantly faster; the difference can typically
be 10\% to 25\%. It is therefore better to use single precision. What
you can do once for the physical problem you want to study is run
the same calculation in single precision and in double precision on
your system and compare the seismograms. If they are identical (and
in most cases they will), you can select single precision for your
future runs.\newline

@@

\noindent
Installation instructions for IBM BlueGene (from April 2013):\newline

@@

\noindent The most relevant are the -qarch and -qtune flags, otherwise
if these flags are set to ``auto'' then they are wrongly assigned
to the architecture of the frond-end node, which is different from
that on the compute nodes. You will need to set these flags to the
right architecture for your BlueGene compute nodes, which is not necessarily
``qp''; ask your system administrator. On some machines if is necessary
to use -O2 in these flags instead of -O3 due to a compiler bug of
the XLF version installed. We thus suggest to first try -O3, and then
if the code does not compile or does not run fine then switch back
to -O2. The debug flags (-g, -qfullpath) do not influence performance
but are useful to get at least some insights in case of problems.\newline

\noindent Before running \texttt{configure}, select the XL Fortran
compiler by typing \texttt{module load bgq-xl/1.0} or \texttt{module
load bgq-xl} (another, less efficient option is to load the GNU compilers
using \texttt{module load bgq-gnu/4.4.6} or similar).\newline

@@

\noindent \underline{Older installation instruction for IBM BlueGene, from 2011:}\newline

@@

\begin{enumerate}
\setcounter{enumi}{-1}
\item Install \texttt{Doxygen} \underline{and} \texttt{graphviz} (the two are usually in the package manager of classic Linux distribution).
\item Run in the terminal : \texttt{doxygen -g}, which creates a \texttt{Doxyfile} that tells doxygen what you want it to do.
\item Edit the Doxyfile. Two Doxyfile-type files have been already committed in the directory \newline
\noindent \texttt{specfem3d/doc/Call\_trees}:

@@

If you want to develop new features in the code, and/or if you want to make small changes, improvements, or bug fixes, you are very welcome to contribute. To do so, i.e. to access the development branch of the source code with read/write access (in a safe way, no need to worry too much about breaking the package, there are CI tests based on BuildBot, Travis-CI and Jenkins in place that are checking and validating all new contributions and changes), please visit this Web page:\newline
\url{https://github.com/SPECFEM/specfem3d/wiki}

### 2022-11-12 doc/USER_MANUAL/04_creating_databases.tex
updates tex files (\\ to \newline) for better pandoc conversions to wiki pages

After using \texttt{xmeshfem3D} or \texttt{xdecompose\_mesh}, the
next step in the workflow is to compile \texttt{xgenerate\_}~\\
 \texttt{databases}. This program is going to create all the missing
information needed by the SEM solver.

@@

Before running \texttt{xgenerate\_databases}, a number of parameters
need to be set in the main parameter \texttt{Par\_file} located in
the subdirectory \texttt{DATA}:\\

@@

\item [\texttt{ADIOS\_ENABLED}] Turn this flag on to enable ADIOS. If set to \texttt{.false.}, subsequent ADIOS
parameters will not be considered.
\item [\texttt{ADIOS\_FOR\_DATABASES}] Turn this flag on to use ADIOS for xmeshfem3D output and
xgenerate\_database input.
\item [\texttt{ADIOS\_FOR\_MESH}]  Turn this flag on to use ADIOS for generated databases.
\item [\texttt{ADIOS\_FOR\_FORWARD\_ARRAYS}] Turn this flag on to read and write forward arrays using ADIOS.
\item [\texttt{ADIOS\_FOR\_KERNELS}] Turn this flag on to produce ADIOS kernels that can later be visualized with the ADIOS version of combine\_vol\_data.
\end{description}
There are quite a few more parameters to change the default setup of your runs. Please check the comments in the \texttt{DATA/Par\_file} directly for further explanations.\\

@@

The database generator \texttt{xgenerate\_databases}, as well as the
internal mesher \texttt{xmeshfem3D}, are trying to evaluate the value
of $\Delta t$ for empirically chosen Courant numbers $C\sim0.3$.
If you used the mesher \texttt{xmeshfem3D} to generate your mesh,
you should set the value suggested in \texttt{OUTPUT\_FILES/output\_mesher.txt}
file, which is created after the mesher completed. In case you used
CUBIT to create the mesh, you might use an arbitrary value when running
\texttt{xgenerate\_databases} and then use the value suggested in
the ~\\
 \texttt{OUTPUT\_FILES/output\_mesher.txt} file after the database
generation completed. Note that the implemented Newmark time scheme
uses this time step globally, thus your simulations become more expensive
for very small mesh elements in high wave-speed regions. Please be
aware of this restriction when constructing your mesh in Chapter~\ref{cha:Mesh-Generation}.

>>>>

After using \texttt{xmeshfem3D} or \texttt{xdecompose\_mesh}, the
next step in the workflow is to compile \texttt{xgenerate\_}~\newline
 \texttt{databases}. This program is going to create all the missing
information needed by the SEM solver.

@@

Before running \texttt{xgenerate\_databases}, a number of parameters
need to be set in the main parameter \texttt{Par\_file} located in
the subdirectory \texttt{DATA}:\newline

@@

\item [\texttt{ADIOS\_ENABLED}] Turn this flag on to enable ADIOS. If set to \texttt{.false.}, subsequent ADIOS
parameters will not be considered.
\item [\texttt{ADIOS\_FOR\_DATABASES}] Turn this flag on to use ADIOS for xmeshfem3D output and
xgenerate\_database input.
\item [\texttt{ADIOS\_FOR\_MESH}]  Turn this flag on to use ADIOS for generated databases.
\item [\texttt{ADIOS\_FOR\_FORWARD\_ARRAYS}] Turn this flag on to read and write forward arrays using ADIOS.
\item [\texttt{ADIOS\_FOR\_KERNELS}] Turn this flag on to produce ADIOS kernels that can later be visualized with the ADIOS version of combine\_vol\_data.
\end{description}
There are quite a few more parameters to change the default setup of your runs. Please check the comments in the \texttt{DATA/Par\_file} directly for further explanations.\newline

@@

The database generator \texttt{xgenerate\_databases}, as well as the
internal mesher \texttt{xmeshfem3D}, are trying to evaluate the value
of $\Delta t$ for empirically chosen Courant numbers $C\sim0.3$.
If you used the mesher \texttt{xmeshfem3D} to generate your mesh,
you should set the value suggested in \texttt{OUTPUT\_FILES/output\_mesher.txt}
file, which is created after the mesher completed. In case you used
CUBIT to create the mesh, you might use an arbitrary value when running
\texttt{xgenerate\_databases} and then use the value suggested in
the ~\newline
 \texttt{OUTPUT\_FILES/output\_mesher.txt} file after the database
generation completed. Note that the implemented Newmark time scheme
uses this time step globally, thus your simulations become more expensive
for very small mesh elements in high wave-speed regions. Please be
aware of this restriction when constructing your mesh in Chapter~\ref{cha:Mesh-Generation}.
